Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-10 paper.tex
ARG section typo

For our purposes, an ARG is a realisation of the coalescent with
recombination, in the Griffiths (little ARG) sense.
As described in detail by~\cite{kelleher2016efficient}, Hudson's algorithm
works by dynamically generating and traversing a little ARG.
The graph is not explicitly represented in memory, but is partially
present through the extant lineages and the ancestral material they carry
over time. We do not output the graph directly, but
rather store the information required to recover the genealogical
history as nodes and edges in a tree sequence (see the \nameref{sec-ts} section),
or ``coalescence records'' in original terminology~\citep{kelleher2016efficient}.
This is far more efficient than outputting the simulated ARG in its entirety.
For a given scaled recombination rate $\rho$
(setting aside the dependency on the sample size $n$)
we know from Eq.~\eqref{eqn-hsw-bound} that the number of nodes
in an ARG is $O(\rho^2)$,
whereas the size of the tree sequence encoding is
$O(\rho)$~\citep{kelleher2016efficient}.
This difference between a
quadratic and a linear dependency on $\rho$ is profound, and shows why
large simulations cannot output an ARG in practice.

>>>>

For our purposes, an ARG is a realisation of the coalescent with
recombination, in the Griffiths (little ARG) sense.
As described in detail by~\cite{kelleher2016efficient}, Hudson's algorithm
works by dynamically generating and traversing a little ARG.
The graph is not explicitly represented in memory, but is partially
present through the extant lineages and the ancestral material they carry
over time. We do not output the graph directly, but
rather store the information required to recover the genealogical
history as nodes and edges in a tree sequence (see the \nameref{sec-ts} section),
or ``coalescence records'' in the original terminology~\citep{kelleher2016efficient}.
This is far more efficient than outputting the simulated ARG in its entirety.
For a given scaled recombination rate $\rho$
(setting aside the dependency on the sample size $n$)
we know from Eq.~\eqref{eqn-hsw-bound} that the number of nodes
in an ARG is $O(\rho^2)$,
whereas the size of the tree sequence encoding is
$O(\rho)$~\citep{kelleher2016efficient}.
This difference between a
quadratic and a linear dependency on $\rho$ is profound, and shows why
large simulations cannot output an ARG in practice.
